### 2019-03-18 thesis_proposal_1/Chapters/1_Introduction.tex
abstract summary

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

\section{Main Section 1}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Main Section 2}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

>>>>

\label{Chapter:Introduction}

@@

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------

### 2019-03-18 thesis_proposal_1/main.tex
min feature
abstract summary

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: onehalfspacing or doublespacing
singlespacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%nolistspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
%parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Thesis Title}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type

@@

The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\

@@

\include{Chapters/1_Introduction}
\include{Chapters/2_ProblmemDefinitionAndMotivation} 
\include{Chapters/3_HypothesisAndResearchQuestions}
\include{Chapters/4_Objectives} 
\include{Chapters/5_TheoreticalFramework}

\include{Chapters/__IntroToLaTeX}

@@

\printbibliography

>>>>

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: onehalfspacing or doublespacing
singlespacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%nolistspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex}
% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%\usepackage[style=apa, backend=biber]{biblatex}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Design of Polymer Solutions for the Fabrication of Conducting Carbon Nano-wires}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type

@@

Carbon fibers are versatile materials composed of carbon chains with a wide range of applications. Carbon nanowires have been fabricated with a photoresist, but little is known about polymers that can produce more conductive carbon nanowires after pyrolysis. FFES or Far field electrospinning is a inexpensive process to produce polymer fibers, but with low accuracy due to electric instabilities. Near field electrospinning (NFES) is similar to FFES, but with a reduced distance between the fiber source and the collector and higher precision. Various polymer solutions have being tested and measured through NFSE and photopolymerization processes; it was found that it is not possible to predict the behaviour of the electrospinning process, so additional properties are to be considered to achieve a stable process. The properties of the polymer solution can be amended to obtain a electrospun-able, photopolymerizable and pyrolyzable/graphitizable fibers. Analyse the rheology of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them. Design polymer solutions that can be electrospun by NFES, photopolymerized, and then pyrolyzed into conducting carbon nanowires. The use of the newly designed polymer solution within the NFES-Photopolymerization-Pyrolysis process can be amended to achieve mass scale manufacturing of carbon nanowires in a cheap, continuous, simple and reproducible manner. The new/tailored polymer solution can be used to synthesize carbon nanowires with high conductive properties and reduced thickness. \\

@@

\include{Chapters/1_Introduction}
\include{Chapters/2_ProblmemDefinitionAndMotivation} 
\include{Chapters/3_HypothesisAndResearchQuestions}
\include{Chapters/4_Objectives} 
\include{Chapters/5_TheoreticalFramework}
\include{Chapters/6_Methodology}
\include{Chapters/7_WorkPlan}

%\include{Chapters/__IntroToLaTeX}

@@

\printbibliography[title={References}]
